Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
a

\vspace{-3mm}
In this supplementary material, we provide:\vspace{-0.1in}
\begin{enumerate}
\item The closed-form solution of the sparse coding problem (6) in the main paper.
\vspace{-3mm}
\item More denoising results on the real noisy images in dataset \cite{ncwebsite}.
\vspace{-3mm}
\item More denoising results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
\vspace{-3mm}
\item More denoising results on the 60 cropped real noisy images (with mean image of 500 shots as ``ground truth") from dataset \cite{crosschannel2016}.
\end{enumerate}

>>>>

\vspace{-2mm}
In this supplementary material, we provide:\vspace{-0.1in}
\begin{enumerate}
\item The closed-form solution of the sparse coding problem (6) in the main paper.
\vspace{-2mm}
\item More denoising results on the real noisy images in dataset \cite{ncwebsite}.
\vspace{-2mm}
\item More results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
\vspace{-2mm}
\item More results on the 60 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
\end{enumerate}
